Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-12-20 paper/main.tex
top sheave then cat sheaf

\subsection{Sheaves}
\label{sec:related-work:continuity:sheaves}
Sheaves provide a mathematical abstraction of data, the space it lives over, and relationships between subsets. Sheaves can be thought of as an "algebraic data structure" \cite{ghristElementaryAppliedTopology2014} for data that lives over topological spaces. A presheaf  $\sheaf$ applied to fiber bundles is a map from an open set in a topological space, such $\openset \subset \dbase$, to the set of sections 
\begin{equation}
  \label{eq:atct:presheaf}
  \sheafc: \opensetc \textcolor{sheaf}{\rightarrow} \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}
\end{equation}
over that openset \cite{spanier1989algebraic,SheafMathematics2021,nlab:presheaf}. The presheaf preserves the inclusion maps $\iota$ between open sets and the restriction maps $\iota^*$ between the sets of sections over that open sets. 
\begin{equation}
  \label{eq:related-work:continuity:presheaf}
  \begin{tikzcd}[column sep=small]
    {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}} & {} & {\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}} \arrow[ll, "\iota^*"', hook', color=set] \\& &\\
    \opensetc_1 \arrow[uu, "\sheafc_{\dtotalc}", color=sheaf] \arrow[rr, "\iota"', hook, color=base] & {} \arrow[uu, "\sheafc_{\dtotalc}" description, dotted, color=sheaf] & \opensetc_2 \arrow[uu, "\sheafc_{\dtotalc}"', color=sheaf]                    
    \end{tikzcd}
\end{equation}

This means that a smaller space $\openset_1$ is included in a larger space $\openset_2$ and a function $\dsection \in \Gamma(\openset, \dtotal\restriction_{\openset})$ that is continuous over a larger space $\openset_2$ is continuous over a subspace $\openset_1 \subset\openset_2$.

A presheaf \sheafc\, as introduced in \autoref{eq:related-work:continuity:presheaf}, is a contravariant functor\cite{nlab:presheaf} from a category to a set. 
\begin{equation}
  \label{eq:actc:sheaf}
 \sheafc: \textcolor{source}{\mathcal{C}^{op}} \rightarrow \textcolor{target}{\textbf{Set}}
\end{equation}

A presheaf $\sheaf(\dtotal)$ over a limit of open sets that contain a point $\dbasepoint \in \dbase$ is approximately the same as a sheaf over a point \dbasepoint\ and is called the stalk\cite{StalkSheaf2019} 
\begin{equation}
  \label{eq:atct:stalk}
  \sheafc(\dbasec)\restriction_{\dbasepointc}\coloneqq \lim\limits_{\opensetc\ni \dbasepointc} \Gamma(\opensetc, \dtotalc\restriction_{\opensetc}) 
\end{equation}

Sheaves are presheafs where sections are continuous over all unions of open sets in $\dbase$\cite{harder2008lectures, spanier1989algebraic, nlab:sheaf}. This means that a section which is defined over a stalk $\dsection \in \sheaf(\dbase)\vert_{\dbasepoint_i}$ and evaluated at a point $\dbasepoint_j$ is equal to a section in the stalk over that point $\dsection_{dbasepoint_i}\vert_{dbasepoint_j} = \dsection_{\dbasepoint_j}$

We can define natural transforms, introduced in \autoref{eq:related-work:equivariance:natural-transform}, between sheaves over different spaces, for example spaces representing the topology of the data and the graphic, because sheaves can be moved over different topological spaces if there is a map between those spaces. 
Given a map $\textcolor{functor}{f}:\textcolor{source}{X} \textcolor{functor}{\rightarrow} \textcolor{target}{Y}$ between topological spaces $\textcolor{source}{X}, \textcolor{target}{Y}$ and sheaves on each space $\sheafc_{\textcolor{source}{X}}, \sheafc_{\textcolor{target}{Y}}$, we can construct the pullback functor $f^*$ and pushforward functor $f_*$ \cite{harder2008lectures} such that the following diagram commutes
\begin{equation}
  \label{eq:atct:pullback-pushforward}
  abc
\end{equation}

>>>>

\subsection{Sheaves}
\label{sec:related-work:continuity:sheaves}
Sheaves provide a mathematical abstraction of data, the space it lives over, and relationships between subsets. Sheaves can be thought of as an "algebraic data structure" \cite{ghristElementaryAppliedTopology2014} for data that lives over topological spaces. A presheaf  $\sheaf$ applied to fiber bundles is a map from an open set in a topological space, such as $\openset \subset \dbase$ where $(\mathcal{T}, \dbase)$ is a topological space, to the set of sections of a bundle $\dtotal$ over that openset \cite{spanier1989algebraic,SheafMathematics2021,nlab:presheaf}.
\begin{equation}
  \label{eq:atct:presheaf}
  \sheafc: \opensetc \textcolor{sheaf}{\rightarrow} \cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}
\end{equation}
The presheaf preserves the inclusion maps $\iota$ between open sets and the restriction maps $\iota^*$ between the sets of sections over that open sets. 
\begin{equation}
  \label{eq:related-work:continuity:presheaf}
  \begin{tikzcd}[column sep=small]
    {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}} & {} & {\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}} \arrow[ll, "\iota^*"', hook', color=set] \\& &\\
    \opensetc_1 \arrow[uu, "\sheafc_{\dbasec}", color=sheaf] \arrow[rr, "\iota"', hook, color=base] & {} \arrow[uu, "\sheafc_{\dbasec}" description, dotted, color=sheaf] & \opensetc_2 \arrow[uu, "\sheafc_{\dbasec}"', color=sheaf]                    
    \end{tikzcd}
\end{equation}

This means that a smaller space $\openset_1$ is included in a larger space $\openset_2$ and a function in a set of global sections over a bundle $\dsection \in \Gamma(\openset_2, \dtotal\restriction_{\openset2})$ that is continuous over a larger space $\openset_2$ is continuous when restricted to a subspace $\dsection \in \Gamma(\openset_1,\dtotal\restriction_{\openset2}),\openset_1 \subset\openset_2$.

A presheaf $\sheaf$ over a limit of open sets that contain a point $\dbasepoint \in \dbase$ is approximately the same as a sheaf over a point \dbasepoint\ and is called the stalk\cite{StalkSheaf2019} 
\begin{equation}
  \label{eq:atct:stalk}
  \sheafc(\dbasec)\restriction_{\dbasepointc}\coloneqq \lim\limits_{\opensetc\ni \dbasepointc} \Gamma(\opensetc, \dtotalc\restriction_{\opensetc}) 
\end{equation}

Sheaves are presheafs where sections are continuous over all unions of open sets in $\dbase$\cite{harder2008lectures, spanier1989algebraic, nlab:sheaf}. This means that a section which is defined over a stalk $\dsection \in \sheaf(\dbase)\vert_{\dbasepoint_i}$ and evaluated at a point $\dbasepoint_j$ is equal to a section in the stalk over that point $\dsection_{\dbasepoint_i}\vert_{\dbasepoint_j} = \dsection_{\dbasepoint_j}$

In category theory, a presheaf \sheafc\, is generalized to be a contravariant functor\cite{nlab:presheaf} from a category to a set. 
\begin{equation}
  \label{eq:actc:sheaf}
 \sheafc: \textcolor{source}{\mathcal{C}^{op}} \rightarrow \setc
\end{equation}
We can define natural transforms, introduced in \autoref{eq:related-work:equivariance:natural-transform}, between sheaves over different spaces, for example spaces representing the topology of the data and the graphic, because sheaves can be moved over different topological spaces if there is a map between those spaces. 
Given a map $\textcolor{functor}{f}:\textcolor{source}{X} \textcolor{functor}{\rightarrow} \textcolor{target}{Y}$ between topological spaces $\textcolor{source}{X}, \textcolor{target}{Y}$ and sheaves on each space $\sheafc_{\textcolor{source}{X}}, \sheafc_{\textcolor{target}{Y}}$, we can construct a pullback functor $f^*$ and pushforward functor $f_*$ \cite{harder2008lectures} that can be composed with the sheaf functors. 
\begin{equation}
  \label{eq:atct:pullback-pushforward}
  \begin{tikzcd}[row sep=huge]
    \sheafc_{\textcolor{source}{X}}(\textcolor{source}{X}) \arrow[rr, "\textcolor{functor}{f_*}", color=functor]                            &  & (\textcolor{functor}{f_*}\sheafc_{\textcolor{source}{X}})(\textcolor{target}{Y})    \\
    \textcolor{source}{X} \arrow[rr, "\textcolor{functor}{f}", color=functor] \arrow[u, "\sheaf_{\textcolor{source}{X}}", color=sheaf] \arrow[d, dashed, color=sheaf] &  & \textcolor{target}{Y} \arrow[d, "\sheaf_{\textcolor{target}{Y}}", color=sheaf] \arrow[u, dashed, color=sheaf] \\
    (\textcolor{functor}{f^*}\sheafc_{\textcolor{target}{Y}})(\textcolor{source}{X}) \arrow[rr, "\textcolor{functor}{f^*}", color=functor]  &  & \sheafc_{\textcolor{target}{Y}}(\textcolor{target}{Y})                             
  \end{tikzcd}
\end{equation}
As shown in \autoref{eq:atct:pullback-pushforward}, the composition $f_*\sheaf_{X}$ modifies the functor $\sheaf_{X}$ such that sections $\dsection \in \sheaf_{X}
